Verifying Demonstrations

### 2018-05-22 paper/DistanceBounding.tex

The main security requirements of \ac{DB} protocols can be summarized as follows:
\begin{itemize}
    % XXX Describe the DB frauds in more detail, i.e. explain them.
  \item \ac{DBMF}: the adversary illegitimately authenticates, possibly using a far-away honest prover.
  \item\ac{DBTF}: a malicious prover helps an accomplice to authenticate.
    \item \ac{DBDF}: a legitimate but malicious prover wants to fool the verifier on the distance between them.
  \item \ac{DBDH}: similar to \ac{DBDF}, sometimes using the presence of an honest prover close to the verifier.
  \item \ac{DBIF}: the adversary plays against a simplified version of the protocol without any distance estimation.
\end{itemize}
There are two lines of attempts at formalizing the above properties: one by \citet{DB-BMV} and another by \citet{DB-DFKO}.

The majority of the existing \ac{DB} protocols are symmetric and thus requires an honest verifier.
Indeed, in this context it does not make sense to protect against the verifier as he can impersonate easily the prover as he has a knowledge of his secret key.
There has been less work done in the domain of asymmetric (or public-key) \ac{DB} protocols.
Unfortunately, our setting requires a public-key \ac{DB} protocol with a \emph{malicious verifier} who will try to \emph{impersonate the prover}.
The verifier might also try to track the provers and map their identities to their actions, thus we also require privacy.
This leads to the requirement of a \ac{DB} \ac{ZKPK}, or simply \ac{DBPK}, with resistance to all the frauds mentioned above as well as against this verifier 
who will attempt to impersonate the prover.
More specifically, we must combine such \iac{DB} with anonymous credentials, which we will describe next.
The anonymous credential system will affect what properties we require of the \ac{DBPK}, (\eg that it must be \iac{PKE} for discrete logarithms).
%Seb: I have created the acronym DBPK in bibsp.sty

>>>>

The main security requirements of \ac{DB} protocols can be summarized as follows:
\begin{itemize}
  \item \ac{DBMF}: the adversary illegitimately authenticates, possibly using a 
    far-away honest prover.
  \item\ac{DBTF}: a malicious prover helps an accomplice to authenticate.
    \item \ac{DBDF}: a legitimate but malicious prover wants to fool the verifier on the distance between them.
  \item \ac{DBDH}: similar to \ac{DBDF}, sometimes using the presence of an honest prover close to the verifier.
  \item \ac{DBIF}: the adversary plays against a simplified version of the protocol without any distance estimation.
\end{itemize}
\daniel{Describe the DB frauds in more detail, i.e. explain them.}
There are two lines of attempts at formalizing the above properties: one by \citet{DB-BMV} and another by \citet{DB-DFKO}.

The majority of the existing \ac{DB} protocols are symmetric and thus requires an honest verifier.
Indeed, in this context it does not make sense to protect against the verifier as he can impersonate easily the prover as he has a knowledge of his secret key.
There has been less work done in the domain of asymmetric (or public-key) \ac{DB} protocols.
Unfortunately, our setting requires a public-key \ac{DB} protocol with a \emph{malicious verifier} who will try to \emph{impersonate the prover}.
The verifier might also try to track the provers and map their identities to their actions, thus we also require privacy.
This leads to the requirement of a \ac{DB} \ac{ZKPK}, or simply \ac{DBPK}, with resistance to all the frauds mentioned above as well as against this verifier 
who will attempt to impersonate the prover.
More specifically, we must combine such \iac{DB} with anonymous credentials, which we will describe next.
The anonymous credential system will affect what properties we require of the \ac{DBPK}, (\eg that it must be \iac{PKE} for discrete logarithms).

### 2018-05-22 paper/RelatedWork.tex
coincoin

The seemingly most commonly used method for counting crowds at protests is \emph{Jacob's method}~\cite[c.f.][]{%
  2016DemonstrationsInSeoul,%
  BBCHowToCountProtestNumbers,%
  HowWillWeKnowTrumpInauguralCrowdSize,%
  TheXManMarch,%
  TheCrowdNumbersGame,%
}.
It is a manual method devised in the 1960s relying on aerial photos of the event.
The verifier divides the protest venue into regions and then estimates the density of the crowd in the different regions and finally sums them up to get an estimate of the global count.
Clearly this method is prone to errors as it is based on estimates.
It provides universal verifiability (\cref{UniversalVerif}) since anyone can redo the counting using the same photos.
However, it is difficult to achieve individual verifiability (\cref{IndividualVerif}) using this method since it is hard to verify that oneself is indeed in any of the photos\footnote{It is of course possible with very detailed photos, but not currently realistic to do with aerial photos.}.
We can argue that it also achieves eligibility (\cref{EligibilityVerif}) if all the photos are taken at the same point in time with no overlap, since then no one can be counted twice.
Unfortunately, we can only get the peak participation with this method.
When it comes to spatial and temporal eligibility, we have to rely on pictures (\eg by determining from the photos themselves when and where the they were taken).
However, this is prone to cheating and the best we can do is to employ forensic methods to try to detect any modifications or other attempts at fraud.
%Seb: maybe we should also give information about the privacy level reached by this different method

Among more recent methods, there is an application called CrowdSize~\cite{CrowdSize} that can estimate the size of a crowd 
based on a selected space.
Once the user has specified the zone, he selects one of three pre-set density estimates: light, medium or dense.
%Seb: what are the meaning of the choice of density estimates, it is a way to specify an apriori assumption about the density of the crowd or to choose between a min, average, max estimates?
This is similar to the method usually used by police (\eg for the protests in Seoul):
\blockcquote{2016DemonstrationsInSeoul}{%
  \textins*{p}olice presume\textins*{d} that, when sitting, six people would 
  fill a space of 
  3.3 square meters
  \textelp{}
  The same area would hold nine or 10 people when standing%
}.
This method is not verifiable unless the user takes a picture of the crowd, in which case it inherits the verifiability properties of the previous method.

@@

>>>>

\subsection{Crowd counting methods}

The seemingly most commonly used method for counting crowds at protests is \emph{Jacob's method}~\cite[c.f.][]{%
  2016DemonstrationsInSeoul,%
  BBCHowToCountProtestNumbers,%
  HowWillWeKnowTrumpInauguralCrowdSize,%
  TheXManMarch,%
  TheCrowdNumbersGame,%
}.
It is a manual method devised in the 1960s relying on aerial photos of the event.
The verifier divides the protest venue into regions and then estimates the density of the crowd in the different regions and finally sums them up to get an estimate of the global count.
Clearly this method is prone to errors as it is based on estimates.
It provides universal verifiability (\cref{UniversalVerif}) since anyone can redo the counting using the same photos.
However, it is difficult to achieve individual verifiability (\cref{IndividualVerif}) using this method since it is hard to verify that oneself is indeed in any of the photos\footnote{It is of course possible with very detailed photos, but not currently realistic to do with aerial photos.}.
We can argue that it also achieves eligibility (\cref{EligibilityVerif}) if all the photos are taken at the same point in time with no overlap, since then no one can be counted twice.
Unfortunately, we can only get the peak participation with this method.
When it comes to spatial and temporal eligibility, we have to rely on pictures (\eg by determining from the photos themselves when and where the they were taken).
However, this is prone to cheating and the best we can do is to employ forensic methods to try to detect any modifications or other attempts at fraud.
\seb{maybe we should also give information about the privacy level reached by 
  this different method}

Among more recent methods, there is an application called CrowdSize~\cite{CrowdSize} that can estimate the size of a crowd 
based on a selected space.
Once the user has specified the zone, he selects one of three pre-set density estimates: light, medium or dense.
\seb{what are the meaning of the choice of density estimates, it is a way to 
  specify an apriori assumption about the density of the crowd or to choose 
  between a min, average, max estimates?}
This is similar to the method usually used by police (\eg for the protests in Seoul):
\blockcquote{2016DemonstrationsInSeoul}{%
  \textins*{p}olice presume\textins*{d} that, when sitting, six people would 
  fill a space of 
  3.3 square meters
  \textelp{}
  The same area would hold nine or 10 people when standing%
}.
This method is not verifiable unless the user takes a picture of the crowd, in which case it inherits the verifiability properties of the previous method.

@@

\input{LocationProofs.tex}

### 2018-05-22 paper/SystemModel.tex

\begin{definition}[Participation-proof share]
  A \emph{participation-proof share} \(w = (pid, cid, t, l, wid)\) is a tuple 
  where
  \(cid, t, l\) are as in \cref{DefProtest},
  \(pid\) is unique for a protester--\(cid\) pair, and
  \(wid\) is unique for a witness--protester pair.
  We let \(W\) be the set of all proof shares.
\end{definition}
%Sonja asks: do the same pair of people (witness-protester) get the
%same wid on a different protest? The pid is unique for protester-cid
%pair thus the id of a protester at a particular protest. Pid is thus
%derived from the protester id (which has no term) and the protest id
%(cid)? In analogy, wid is derived from pid (and thus cid) of both
%participants, protesters i and j, say, where i witnesses j at cid and
%simultaneously symmetrically j witnesses i?
%Using wid and w is confusing since we changed the terminology to use
%proof shares instead of the previous witness (as in testimony, not
%person). wid sounds like it would be the id of the witness person,
%pid sounds like it would be the id of the protester being witnessed,
%we have defined neither and they might not be needed, but it is
%confusing to read.

>>>>

\begin{definition}[Participation-proof share]
  A \emph{participation-proof share} \(w = (pid, cid, t, l, wid)\) is a tuple 
  where
  \(cid, t, l\) are as in \cref{DefProtest},
  \(pid\) is unique for a protester--\(cid\) pair, and
  \(wid\) is unique for a witness--protester pair.
  We let \(W\) be the set of all proof shares.
\end{definition}
\sonja{do the same pair of people (witness-protester) get the
same wid on a different protest? The pid is unique for protester-cid
pair thus the id of a protester at a particular protest. Pid is thus
derived from the protester id (which has no term) and the protest id
(cid)? In analogy, wid is derived from pid (and thus cid) of both
participants, protesters i and j, say, where i witnesses j at cid and
simultaneously symmetrically j witnesses i?
Using wid and w is confusing since we changed the terminology to use
proof shares instead of the previous witness (as in testimony, not
person). wid sounds like it would be the id of the witness person,
pid sounds like it would be the id of the protester being witnessed,
we have defined neither and they might not be needed, but it is
confusing to read.}

### 2018-05-22 paper/intro.tex

Existing methods for crowd-counting vary significantly in terms of approaches (we will review them in details in \cref{RelatedWork}).
However, most of them lack precision (\ie they have large error margins) and they can only give an estimate for a particular snapshot in time (\eg at the peak of the event). 
In particular, the existing methods cannot reliably estimate the cumulative participation count --- at least not without counting some persons multiple times, which in turn increases the error of the estimation.
In addition, they also lack verifiability. 
%as everyone has to trust the entity responsible for performing the counting.
%Sonja says: I commented this out as it doesn't apply to all. Sometimes you have to trust the data but can count yourself (pictures) or can even take pictures yourself but that's not really verifiability either.

Finally, one important observation about crowd-counting that has not been adequately addressed in the design of current crowd-counting solutions is that it is actually an adversarial setting. 
Indeed, going back to our example, Alice the activist has an incentive to increase the tallied number of participants, whereas Grace (and possibly other entities) have an incentive to decrease it.
In this case, we are left with two options: either we trust Alice or Grace (or 
another third party), or we have to be able to verify their claims ourselves.
In this paper, our main objective is to provide a scheme preventing both Alice and Grace from cheating (\ie their claim should be verifiable).
To solve this issue, we need a verifiable participation count that can resist Sybil attacks while still preserving the participants'
privacy to the extent possible given their physical presence at the protest. 
More precisely, our solution will not be able to prevent an observer (physically present or looking at photos or videos) from recognizing a particular individual at a protest. 
Nonetheless, we can ensure that none of the digital traces generated by a participant in our scheme can be associated with their identity and that their actions are also unlinkable.
%Sonja says: what actions do we refer to here?

%Seb: to do complete the contributions
\emph{Contributions.} In this paper, our main contribution is to propose \PRIVO, a privacy-preserving scheme providing a way to securely estimate crowd count in protests.
Additionally, this verification system does not incur any additional risk to protesters' privacy beyond the ones related to physically participating in the protest in the first place.

@@

\emph{Limitations and assumptions.} Some of the assumptions that are required 
for implementing our proposition are not yet realized (see \cref{assumptions} 
for more detailed descriptions). In particular, not all (or even many) 
protesters, especially in countries with oppressive regimes, currently possess 
smartphones.
In addition, digital certificates signed by a central authority are not yet widely available and if we rely on government-issued credentials, we cannot prevent the government from performing Sybil attacks --- since it can issue arbitrarily many \emph{valid} credentials. 
%Seb: maybe to prevent the above issue, we could require the individual to generate his secret key and only use the authority to obtain a certification on his public key (in the spirit of blind signature)
In this case, it does not make sense to verify any pro-government protests in 
which Grace's authoritarian regime wants to organize a pro-regime protest to 
demonstrate its wide support, 
\eg~\cite{AlJazeeraOnVenezuela2017,VenezuelanStateWorkersCalledToParticipate}.
Finally, achieving distance-bounding protocols on smartphones is currently not 
feasible within a meaningful range of distance needed for our scenario.
They lack the required hardware to do the distance bounding fast enough.

@@

%Seb: to do, update the outline
\emph{Outline.} The paper is organized as follows. First, we define and 
formalize the notion of protest and discuss its relationship with electronic 
voting (\cref{SystemModel}).  We then present the desired security properties 
for such a system (\cref{Properties}) and subsequently discuss related work in 
terms of these properties (\cref{RelatedWork}). We give the relevant background 
on the building blocks of our solution, including our proposal for 
distance-bounding anonymous credentials that cope with a malicious 
(impersonating) verifier (\cref{BuildingBlocks}). \PRIVO, the protocol 
constructed from the building blocks, is presented next (\cref{Protocol}) and we 
analyze its security and privacy (\cref{SecurityAnalysis}) as well as 
performance and implementation issues (\cref{PerformanceAnalysis}). We conclude 
with a discussion.

>>>>

Existing methods for crowd-counting vary significantly in terms of approaches (we will review them in details in \cref{RelatedWork}).
However, most of them lack precision (\ie they have large error margins) and they can only give an estimate for a particular snapshot in time (\eg at the peak of the event). 
In particular, the existing methods cannot reliably estimate the cumulative participation count --- at least not without counting some persons multiple times, which in turn increases the error of the estimation.
In addition, they also lack verifiability.

Finally, one important observation about crowd-counting that has not been adequately addressed in the design of current crowd-counting solutions is that it is actually an adversarial setting. 
Indeed, going back to our example, Alice the activist has an incentive to increase the tallied number of participants, whereas Grace (and possibly other entities) have an incentive to decrease it.
In this case, we are left with two options: either we trust Alice or Grace (or 
another third party), or we have to be able to verify their claims ourselves.
In this paper, our main objective is to provide a scheme preventing both Alice and Grace from cheating (\ie their claim should be verifiable).
To solve this issue, we need a verifiable participation count that can resist Sybil attacks while still preserving the participants'
privacy to the extent possible given their physical presence at the protest. 
More precisely, our solution will not be able to prevent an observer (physically present or looking at photos or videos) from recognizing a particular individual at a protest. 
Nonetheless, we can ensure that none of the digital traces generated by a participant in our scheme can be associated with their identity and that their actions are also unlinkable.
\sonja{what actions do we refer to here?}

\seb{to do complete the contributions}
\emph{Contributions.} In this paper, our main contribution is to propose \PRIVO, a privacy-preserving scheme providing a way to securely estimate crowd count in protests.
Additionally, this verification system does not incur any additional risk to protesters' privacy beyond the ones related to physically participating in the protest in the first place.

@@

\emph{Limitations and assumptions.} Some of the assumptions that are required 
for implementing our proposition are not yet realized (see \cref{assumptions} 
for more detailed descriptions). In particular, not all (or even many) 
protesters, especially in countries with oppressive regimes, currently possess 
smartphones.
In addition, digital certificates signed by a central authority are not yet widely available and if we rely on government-issued credentials, we cannot prevent the government from performing Sybil attacks --- since it can issue arbitrarily many \emph{valid} credentials. 
\seb{maybe to prevent the above issue, we could require the individual to 
  generate his secret key and only use the authority to obtain a certification 
  on his public key (in the spirit of blind signature)}
In this case, it does not make sense to verify any pro-government protests in 
which Grace's authoritarian regime wants to organize a pro-regime protest to 
demonstrate its wide support, 
\eg~\cite{AlJazeeraOnVenezuela2017,VenezuelanStateWorkersCalledToParticipate}.
Finally, achieving distance-bounding protocols on smartphones is currently not 
feasible within a meaningful range of distance needed for our scenario.
They lack the required hardware to do the distance bounding fast enough.

@@

\seb{to do, update the outline}
\daniel{done?}
\emph{Outline.} The paper is organized as follows. First, we define and 
formalize the notion of protest and discuss its relationship with electronic 
voting (\cref{SystemModel}).  We then present the desired security properties 
for such a system (\cref{Properties}) and subsequently discuss related work in 
terms of these properties (\cref{RelatedWork}). We give the relevant background 
on the building blocks of our solution, including our proposal for 
distance-bounding anonymous credentials that cope with a malicious 
(impersonating) verifier (\cref{BuildingBlocks}). \PRIVO, the protocol 
constructed from the building blocks, is presented next (\cref{Protocol}) and we 
analyze its security and privacy (\cref{SecurityAnalysis}) as well as 
performance and implementation issues (\cref{PerformanceAnalysis}). We conclude 
with a discussion.
